---
title: "Linear Model"
author: "Brianna Olvera"
date: "October 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
myData = read.csv('RawData.csv')
```


# First Model:
SIMS is a function of ARM

```{r}
model1 = lm(SIMS~ARM, data=myData)
summary(model1)
```

predict SIMS fro ARM = 88

```{r}
x = data.frame(GRIP=94, ARM=88)
predSIMS = predict.lm(model1, x)
print(predSIMS)
```

prediction interval:
```{r}
predict(model1, x, interval="predict", level=0.95)
```


# Second model SIMS is a function of GRIP

```{r}
model2 = lm(SIMS~GRIP, data=myData)
summary(model2)
```

predict SIMS fro GRIP = 94

```{r}
predictSIMS2 = predict.lm(model2, x)
print(predictSIMS2)
```


prediction interval:

```{r}
predict(model2, x, interval="predict")
```

# Third Model SIMS is a function of GRIP + ARM

```{r}
model3 = lm(SIMS~GRIP+ARM, data=myData)
summary(model3)
```

predict SIMS fro ARM=88 and GRIP=94

```{r}
predictSIMS3 = predict.lm(model3, x)
print(predictSIMS3)
```


prediction interval for model3

blah .. blah..

comparison between models 1 and 3

```{r}
anova(model1, model3)
```

$H_0$: There is no difference in the models  
$H_A$: there is a difference in the models  

Since the p value is 4.994 we reject the null hypothesis. THere is a difference between model 1 and model 3. We conclude that model 3 is a better fit than model 1.